\section{Related Work}

We first review previous works related to uncertain flow visualization. One group of the methods focused on visualizing the local uncertainty. Glyph-based approaches were discussed in~\cite{conf/visualization/LodhaPSW96, citeulike:4002316}, and texture-based methods were proposed in~\cite{10.1109/VIS.2005.97, botchen:2006:IVUF}. In~\cite{zuk:2008:UBVF}, a method was introduced to visualize uncertainty in bidirectional vector fields. Edge Map was proposed by \cite{10.1109/TVCG.2011.265} to visualize flow fields with quantified spatial and temporal errors. \cite{conf/visualization/SandersonJK04} presented a reaction-diffusion model to visualize the uncertainty. There exist approaches that were designed to visualize global uncertainty which is transported within the flow, such as topology based approaches presented in~\cite{Otto10a, Otto11a}. However, none of the approaches above focused on solving the uncertain particle tracing problem, which is still one of the most popular flow visualization techniques.

In this work, we make use of a Bayesian framework to trace particles in uncertain flows, which has been successfully applied in many disciplines. A thorough analysis of Bayesian modeling is far beyond the scope of the present work. Here we list several previous works which applied Bayesian framework on fiber tracking. \cite{frimanTMI06} presented a Bayesian framework for stochastic white matter tractography. \cite{bjornemoMICCAI02, Brun02whitematter} introduced sequential importance sampling for probabilistic fiber tracking, which was then improved by~\cite{journals/mia/PontabryROSKD13, Zhang20095}.
